Supporting Information for Coherent IR-Hyper-Raman Four Wave Mixing Spectroscopy

### 2024-09-25 paper.tex
kinda there, but not really
working on how to present interference effects in the spectrum.

In this section, we investigate the properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
Coherent spectroscopies are often described using the density matrix formalism, where an n$^{th}$ order density matrix $\rho^{(n)}$ is propagated using the Liouville-von Neumann equation $via$
\begin{equation}\label{LVNE}
	\dot{\rho}^{(n)} = \frac{1}{i \hbar} [H + V(t), \rho^{(n-1)}] + \dot{\rho}^{(n)}_R,
\end{equation}
where $H$ is the (static) system Hamiltonian, $V(t)$ is the field-matter interaction and $\rho_R$ is the relaxation density matrix. \cite{RN455}
In systems where interactions with surroundings are relevant, $\dot{\rho}_R$ becomes a complex function that can be modified to include phenomena such as system-bath interactions, solvent-solute coupling, among others. \cite{Sung2001}
In the limit where input field pulsewidths are much longer than electronic dephasing times and the individual molecule limit is approached, it becomes acceptable to write $\dot{\rho}_R \approx \Gamma \rho$, i.e. exponential relaxation, where $\Gamma$ is the system's dephasing rate. \cite{RN455, Sue1986, Sung2001}
While exponential relaxation is usually an inappropriate description of most physical systems involving solvent-solute interactions,\cite{Sue1986, Yan1988, Li1994, Myers1997} our goal is to introduce simple, quantitative models to understand HDFG response.
Thus, we write $\dot{\rho}_R = \Gamma \rho$.
The exponential relaxation limit has proven useful in investigating the properties of 2D-EV, 2D-VE, and doubly resonant SFG using pulses much longer than electronic dephasing times. \cite{Raschke2002, Gaynor2017}

@@

For consistency with previous reports, we use $\vec{R}$ to denote electric transition dipole moments; $\vec{\mu}$ is reserved for transitions on the ground electronic state. \cite{Tang1970}
Following the approach which gave \autoref{sivegamma} and using the time ordering and state labeling of \autoref{fig:sivewmel2}a, we find
\begin{equation}\label{drgamma_notaylor}
	\gamma_{ijkl} = -\frac{1}{\varepsilon_0} \frac{1}{4D \hbar^3} \sum_{m,n,e,\tilde{v}'} \frac{
		R_{i}^{gv, e\tilde{v}'} 
		R_{j}^{e\tilde{v}',mn} 
		R_{k}^{mn,g0} 
		R_{l}^{g0,gv} 
	}{	\Delta_{e\tilde{v}', gv}
		\Delta_{mn, gv}
		\Delta_{g0,gv}
	}
\end{equation}
where $R_{i}^{ab,cd}$ is the i$^{th}$ element of $\mel{a,b}{\vec{R}}{c,d}$.
To ease readability, we use $\ket{a}$ to refer to ground state vibrational modes and $\ket{\tilde{b}}$ to refer to excited state vibrational modes.
Using our definition of vibronic states, we can write, for example,
$R_{i}^{gv,e\tilde{v}'} = \mel{v}{M_i^{ge}}{\tilde{v}'}$, where $\vec{M}^{ab} = (a|\vec{R}|b)$.\cite{Ziegler1974}
Expanding $\vec{M}^{ij}$ to $\order{Q}$ about the equilibrium point of the ground state potential surface as
$\vec{M}^{ij} = \vec{M}^{ij}_0 + \sum_z \frac{\partial\vec{M}^{ij}}{\partial Q_z} Q_z$
yields $A, B, C$ coefficients similar to those in the Albrecht formalism of Raman scattering, \cite{Albrecht1961, Warshel1977, Ziegler1988} so that
\begin{equation}\label{gammaabc}
		\gamma_{ijkl} \sim \left(A_{ijk} + B_{ijk} + C_{ijk}\right) \frac{\mel{v}{\mu_{l}}{0}} {\Delta_{g0,gv}}
\end{equation}
The $A$ term contains the static ($\order{Q^0}$) transitions (i.e., Condon approximation), the $B$ term depends upon $\order{Q}$ transitions (Herzberg-Teller contributions), and the $C$ term depends on $\order{Q_i Q_j}$ transitions. 
The $C$ term is suppressed in the following discussion as it depends on one and two photon forbidden transitions, making its contribution to $\gamma_{ijkl}$ roughly two orders of magnitude less than $A_{ijk}$. \cite{Ziegler1988, Neddersen1989, Bonang1992}
Note that some reports obtain $A, B$ coefficients through a Herzberg-Teller expansion of the electronic states to expose vibronic couplings via $\partial H / \partial Q$.\cite{HerzbergTeller1933, Petrov1985, Neddersen1989, Baranov1990}
This approach is not used here as the expansion of $\vec{M}^{ij}$ in normal mode coordinates provides sufficient physical insight into HDFG selection rules.

@@

\begin{figure*}[!htbp]
	\centering
	\includegraphics[width=6.66in]{drsive_spectrum.png}
	\caption{Contributions of $A, B$ (\autoref{ABterms_DR}) to HDFG spectrum for a simple two harmonic well system.
		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\Delta = 0.5$, $\omega_1 = \omega_{g1, g0}$, (c, d) real and imaginary parts of terms plotted in (b), respectively.
		The spectra are referenced to $\max{(A+B)}$. 
		It is assumed that $\omega_2 = \omega_3$.
		The vibrational states on the $|g)$ and $|e)$ manifolds are spaced 1600 cm$^{-1}$ apart, with the vibronic states $\ket{e,\tilde{v}'}$ given linewidths of 300 cm$^{-1}$ and $\omega_{eg}$ = 30000 cm$^{-1}$.
		Dotted lines in (b) denote the $\tilde{v}'$ = 0, 1, 2 vibronic resonances. 
		The vibronic one and two photon absorption operators are scaled such that $\abs{B}/\abs{A} \sim$ 0.1, following Chung and Ziegler. \cite{Ziegler1988}
		The Franck-Condon and Herzberg-Teller contributions to each of these terms are found in \autoref{T:contributions}.}
	\label{fig:doubres_spec}
\end{figure*}

@@

\begin{table}[!htbp]
	\caption{\label{T:contributions} Franck-Condon and/or Herzberg-Teller contributions to $A$, $B_1$, $B_2$ terms between $\ket{g,0}$, $\ket{g,1}$ and vibronic states $\ket{e,\tilde{0}}$, $\ket{e,\tilde{1}}$, $\ket{e,\tilde{2}}$ for \autoref{Hamiltonian} with an offset $\Delta = 0.5$.
	The bra and ket labels are written according to their order in $A$, $B_1$, $B_2$ as written in \autoref{ABterms_DR}.
	Closed-form expressions for the Franck-Condon and Herzberg-Teller integrals used here are tabulated in the Supporting Information.}
	\begin{ruledtabular}
		\begin{tabular}{cccc}\label{fcht}
			$2\omega_2$ Electronic Resonance & $\ket{e,\tilde{0}}$ & $\ket{e,\tilde{1}}$ & $\ket{e,\tilde{2}}$\\
			\hline  
			$A$ 
			& $\langle 1 | \tilde{0} \rangle \langle \tilde{0} | 0 \rangle = 0.31 $  
			& $\langle 1 | \tilde{1} \rangle \langle \tilde{1} | 0 \rangle = -0.27 $ 
			& $\langle 1 | \tilde{2} \rangle \langle \tilde{2} | 0 \rangle = -0.04$\\

@@

In the post-resonance region, the amplitude takes on an unexpected lineshape.
This arises due to interference between the real and imaginary parts of $\gamma$ (\autoref{fig:doubres_spec}c, d).
The abnormal lineshapes in both terms arises due to the sign of the Franck-Condon and Herzberg-Teller integrals that drive the output of the vibronic transitions for $\Delta = 0.5$ (\autoref{fcht}), in turn driving significant interference in the overall $\abs{A+B}$ output.
Such effects have been seen elsewhere in spontaneous, surface enhanced hyper-Raman studies. \cite{Milojevich2011}

@@

Evaluating \autoref{contour} for the HDFG pathway above shows\footnote{See the supporting information for more details}

>>>>

In this section, we investigate the properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
Coherent spectroscopies are often described using the density matrix formalism, where an n$^{th}$ order density matrix $\rho^{(n)}$ is propagated using the Liouville-von Neumann equation $via$
\begin{equation}\label{LVNE}
	\dot{\rho}^{(n)} = \frac{1}{i \hbar} [H + V(t), \rho^{(n-1)}] + \dot{\rho}^{(n)}_R,
\end{equation}
where $H$ is the (static) system Hamiltonian, $V(t)$ is the field-matter interaction and $\rho_R$ is the relaxation density matrix. \cite{RN455}
In systems where interactions with surroundings are relevant, $\dot{\rho}_R$ becomes a complex function that can be modified to include phenomena such as system-bath interactions, solvent-solute coupling, among others. \cite{Sung2001}
In the limit where input field pulsewidths are much longer than electronic dephasing times and the individual molecule limit is approached, it becomes acceptable to write $\dot{\rho}^{(n)}_R= \Gamma \rho^{(n)}$, i.e. exponential relaxation, where $\Gamma$ is the system's dephasing rate. \cite{RN455, Sue1986, Sung2001}
While exponential relaxation is usually an inappropriate description of most physical systems involving solvent-solute interactions,\cite{Sue1986, Yan1988, Li1994, Myers1997} our goal is to introduce simple, quantitative models to understand HDFG response.
Thus, we write $\dot{\rho}^{(n)}_R= \Gamma \rho^{(n)}$.
The exponential relaxation limit has proven useful in investigating the properties of 2D-EV, 2D-VE, and doubly resonant SFG using pulses much longer than electronic dephasing times. \cite{Raschke2002, Gaynor2017}

@@

For consistency with previous reports, we use $\vec{R}$ to denote electric transition dipole moments; $\vec{\mu}$ is reserved for transitions on the ground electronic state. \cite{Tang1970}
Following the approach which gave \autoref{sivegamma} and using the time ordering and state labeling of \autoref{fig:sivewmel2}a, we find
\begin{equation}\label{drgamma_notaylor}
	\gamma_{ijkl} = -\frac{1}{\varepsilon_0} \frac{1}{4D \hbar^3} \sum_{m,n,e,\tilde{v}'} \frac{
		R_{i}^{gv, e\tilde{v}'} 
		R_{j}^{e\tilde{v}',mn} 
		R_{k}^{mn,g0} 
		R_{l}^{g0,gv} 
	}{	\Delta_{e\tilde{v}', gv}
		\Delta_{mn, gv}
		\Delta_{g0,gv}
	}
\end{equation}
where $R_{i}^{ab,cd}$ is the i$^{th}$ element of $\mel{a,b}{\vec{R}}{c,d}$.
To ease readability, we use $\ket{a}$ to refer to ground state vibrational modes and $\ket{\tilde{b}}$ to refer to excited state vibrational modes.
Using our definition of vibronic states, we can write, for example,
$R_{i}^{gv,e\tilde{v}'} = \mel{v}{M_i^{ge}}{\tilde{v}'}$, where $\vec{M}^{ab} = (a|\vec{R}|b)$.\cite{Ziegler1974}
Expanding $\vec{M}^{ij}$ to $\order{Q}$ about the equilibrium point of the ground state potential surface as
$\vec{M}^{ij} = \vec{M}^{ij}_0 + \sum_z \frac{\partial\vec{M}^{ij}}{\partial Q_z} Q_z$
yields $A, B, C$ coefficients similar to those in the Albrecht formalism of Raman scattering, \cite{Albrecht1961, Warshel1977, Ziegler1988} so that
\begin{equation}\label{gammaabc}
		\gamma_{ijkl} \sim \left(A_{ijk} + B_{ijk} + C_{ijk}\right) \frac{\mel{v}{\mu_{l}}{0}} {\Delta_{g0,gv}}
\end{equation}
The $A$ term contains the static ($\order{Q^0}$) transitions (i.e., Condon approximation),\cite{Condon1928} the $B$ term depends upon $\order{Q}$ transitions (Herzberg-Teller contributions),\cite{HerzbergTeller1933} and the $C$ term depends on $\order{Q_i Q_j}$ transitions. 
The $C$ term is suppressed in the following discussion as it depends on one and two photon forbidden transitions, making its contribution to $\gamma_{ijkl}$ roughly two orders of magnitude less than $A_{ijk}$. \cite{Ziegler1988, Neddersen1989, Bonang1992}
Note that some reports obtain $A, B$ coefficients through a Herzberg-Teller expansion of the electronic states to expose vibronic couplings via $\partial H / \partial Q$.\cite{HerzbergTeller1933, Petrov1985, Neddersen1989, Baranov1990}
This approach is not used here as the expansion of $\vec{M}^{ij}$ in normal mode coordinates provides sufficient physical insight into HDFG selection rules.

@@

\begin{figure*}[!htbp]
	\centering
	\includegraphics[width=6.66in]{drsive_spectrum.png}
	\caption{Contributions of $A, B$ (\autoref{ABterms_DR}) to HDFG spectrum for a simple two harmonic well system.
		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\Delta = 0.5$, $\omega_1 = \omega_{g1, g0}$, (c, d) real and imaginary parts of terms plotted in (b), respectively.
		The spectra are referenced to $\max{(A+B)}$. 
		It is assumed that $\omega_2 = \omega_3$, and that all molecular parameters used to simulate the spectra are positive.
		The vibrational states on the $|g)$ and $|e)$ manifolds are spaced 1600 cm$^{-1}$ apart, with the vibronic states $\ket{e,\tilde{v}'}$ given linewidths of 300 cm$^{-1}$ and $\omega_{eg}$ = 30000 cm$^{-1}$.
		Dotted lines in (b) denote the $\tilde{v}'$ = 0, 1, 2 vibronic resonances. 
		The vibronic one and two photon absorption operators are scaled such that $\abs{B}/\abs{A} \sim$ 0.1, following Chung and Ziegler. \cite{Ziegler1988}
		The Franck-Condon and Herzberg-Teller contributions to each of these terms are found in \autoref{T:contributions}.}
	\label{fig:doubres_spec}
\end{figure*}

@@

\begin{table}[!htbp]
	\caption{\label{T:contributions} Franck-Condon and/or Herzberg-Teller contributions to $A$, $B_1$, $B_2$ terms between $\ket{g,0}$, $\ket{g,1}$ and vibronic states $\ket{e,\tilde{0}}$, $\ket{e,\tilde{1}}$, $\ket{e,\tilde{2}}$ for \autoref{Hamiltonian} with an offset $\Delta = 0.5$.
	The bra and ket labels are written according to their order in $A$, $B_1$, $B_2$ as written in \autoref{ABterms_DR}.
	The Franck-Condon and Herzberg-Teller integral products tabulated here are plotted in the Supporting Information (Figure S2) as a function of $\Delta$.}
	\begin{ruledtabular}
		\begin{tabular}{cccc}\label{fcht}
			$2\omega_2$ Electronic Resonance & $\ket{e,\tilde{0}}$ & $\ket{e,\tilde{1}}$ & $\ket{e,\tilde{2}}$\\
			\hline  
			$A$ 
			& $\langle 1 | \tilde{0} \rangle \langle \tilde{0} | 0 \rangle = 0.31 $  
			& $\langle 1 | \tilde{1} \rangle \langle \tilde{1} | 0 \rangle = -0.27 $ 
			& $\langle 1 | \tilde{2} \rangle \langle \tilde{2} | 0 \rangle = -0.04$\\

@@

In the post-resonance region, the amplitude takes on an unexpected lineshape.
This arises due to interference between the real and imaginary parts of $\gamma$ (\autoref{fig:doubres_spec}c, d).
The abnormal lineshape arises due to the sign of the Franck-Condon and Herzberg-Teller integrals, as well as the molecular parameters that drive the output of the vibronic transitions.
Such effects have been seen elsewhere in spontaneous, surface enhanced hyper-Raman studies. \cite{Milojevich2011}

The Franck-Condon and Herzberg-Teller integrals can manipulate interference in the total output spectrum as a function of offset (Figure S2).
When the offset is inverted about the origin ($\Delta \rightarrow -\Delta$),

However, the main source of interference in the HDFG spectra arises from the sign of the molecular parameters. 
In the HDFG spectrum presented in \autoref{fig:doubres_spec}, the signs of all molecular parameters are taken to be positive. 
Inverting the sign of one parameter eliminates the interference and restores the expected, purely Lorentzian lineshape.

*orientational averaging
*changing one trivially fixes interference (cf plot above)
*in SI, put examples

@@

Evaluating \autoref{contour} for the HDFG pathway above shows\footnote{See the supporting information for more details.}

### 2024-09-25 si.tex
kinda there, but not really
working on how to present interference effects in the spectrum.

We now will evaluate the polynomial coefficients $P(q)$.
The Hermite polynomials of \autoref{key} can be explicitly written as 
\begin{equation}
\begin{split}
	H_m(q) &= \sum_{s=0}^{\left\lfloor{m/2}\right\rfloor} a_m^{(m-2s)} q^{m-2s} \\
	H_n(q-\Delta) &= \sum_{s=0}^{\left\lfloor{n/2}\right\rfloor}
	a_n^{(n-2s)} (q-\Delta)^{n-2s} \\
		&= \sum_{s=0}^{\left\lfloor{n/2}\right\rfloor} a_n^{(n-2s)} \sum_{l=0}^{n-2s} \left(-\Delta\right)^{n-2s-l} \binom{n-2s}{l} q^l
\end{split}
\end{equation}
where $\left\lfloor n \right\rfloor$ denotes the \textit{floor} of $n$, $\binom{a}{b} = a! / (b!(a-b)!)$, and the Hermite coefficients are\cite{MorseFeshbach}
\begin{equation}
	a_n^{(n-2s)} = n! \frac{(-1)^x 2^{n-2s}}{s!(n-2s)!}.
\end{equation}
Multiplying these terms together give us explicit polynomial coefficients:
\begin{equation}\label{eq:poly_solved}
\begin{split}
	P_{nmk}(q) %&= \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} a_m^{(m-2x)} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} a_n^{(n-2y)} \sum_{l=0}^{n-2y} \Delta^{n-2y-l} \binom{n-2y}{l} q^{l+m-2x+k} \\
	&= \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} c_{xyl} \ q^{l+m-2x+k}, \\
	c_{xyl} &= a_m^{(m-2x)} a_n^{(n-2y)} \left(-\Delta\right)^{n-2y-l} \binom{n-2y}{l}.
\end{split}
\end{equation}
\autoref{eq:poly_solved} is not in standard polynomial form, because our summation is not singular and coefficients in our summation may have the same power. 
Further simplifications can be made to sum to reduce recounting indices, but we do not find these simplifications essential.
Regardless, substituting \autoref{eq:F_solved} and \autoref{eq:poly_solved} into \autoref{eq:analytic_form}, we can now evaluate the solution as:
\begin{equation}\label{eq:general_solution}
	\mel{\tilde{n}}{q^k}{m} = \sqrt{\pi} N_n N_m 
	\exp(-\frac{\Delta^2}{4}) \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+m-2x+k} c_{xyl} H_{l+m-2x+k}\left(i\frac{\Delta}{2}\right).
\end{equation}

@@

\newpage
\section{Impact of displacement, resonance frequencies, vibronic linewidth and molecular parameters on HDFG Spectra}
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/fcht.png}
	\caption{Plots of select (a) Franck-Condon factors and (b) Herzberg-Teller integrals relevant to this manuscript as a function of offset, $\Delta$.} 
	\label{fig:fcht}
\end{figure}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/changedelta.png}
	\caption{The impact of offset, vibrational resonance, and linewidth on HDFG spectra. Parameters for (a,b) follow from Myers et al., whereas parameters for (c,d) follow from Brennan et al.\cite{Myers1982, Brennan2024}} 
	\label{fig:chgdelta}
\end{figure}

@@

\section{Evaluating impact of inhomogeneity on HDFG output}
In this section, the integral
\begin{equation}\label{generalcontour}
	\begin{split}
		\gamma_{ijkl} &= \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)\\
		&= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\eta_{ijkl}}{\left(\Delta_{ga} - \xi\right)\left(\Delta_{ba}+ c\xi\right)} \\
		&= \frac{\eta_{ijkl} \sigma}{\pi} \int_{-\infty}^\infty \mathrm{d}\xi\frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} + c\xi}\\
	\end{split}
\end{equation}
is evaluated for $c=-1$ (electronic state and vibrational state energy fluctuations are anti-correlated) $c=1$ (electronic state and vibrational state energy fluctuations are correlated).

>>>>

We now will evaluate the polynomial coefficients $P(q)$.
The Hermite polynomials of \autoref{key} can be explicitly written as 
\begin{equation}
\begin{split}
	H_m(q) &= \sum_{s=0}^{\left\lfloor{m/2}\right\rfloor} a_m^{(m-2s)} q^{m-2s} \\
	H_n(q-\Delta) &= \sum_{s=0}^{\left\lfloor{n/2}\right\rfloor}
	a_n^{(n-2s)} (q-\Delta)^{n-2s} \\
		&= \sum_{s=0}^{\left\lfloor{n/2}\right\rfloor} a_n^{(n-2s)} \sum_{l=0}^{n-2s} \left(-\Delta\right)^{n-2s-l} \binom{n-2s}{l} q^l
\end{split}
\end{equation}
where $\left\lfloor n \right\rfloor$ denotes the \textit{floor} of $n$, $\binom{a}{b} = a! / (b!(a-b)!)$, and the Hermite coefficients are\cite{MorseFeshbach}
\begin{equation}
	a_n^{(n-2s)} = n! \frac{(-1)^x 2^{n-2s}}{s!(n-2s)!}.
\end{equation}
Multiplying these terms together give us explicit polynomial coefficients:
\begin{equation}\label{eq:poly_solved}
\begin{split}
	P_{nmk}(q) %&= \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} a_m^{(m-2x)} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} a_n^{(n-2y)} \sum_{l=0}^{n-2y} \Delta^{n-2y-l} \binom{n-2y}{l} q^{l+m-2x+k} \\
	&= \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} c_{xyl} \ q^{l+m-2x+k}, \\
	c_{xyl} &= a_m^{(m-2x)} a_n^{(n-2y)} \left(-\Delta\right)^{n-2y-l} \binom{n-2y}{l}.
\end{split}
\end{equation}
\autoref{eq:poly_solved} is not in standard polynomial form, because our summation is not singular and coefficients in our summation may have the same power. 
Further simplifications can be made to sum to reduce recounting indices, but we do not find these simplifications essential.
Regardless, substituting \autoref{eq:F_solved} and \autoref{eq:poly_solved} into \autoref{eq:analytic_form}, we can now evaluate the solution as:
\begin{equation}\label{eq:general_solution}
	\mel{\tilde{n}}{q^k}{m} = \sqrt{\pi} N_n N_m 
	\exp(-\frac{\Delta^2}{4}) \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+m-2x+k} c_{xyl} H_{l+m-2x+k}\left(i\frac{\Delta}{2}\right).
\end{equation}
An alternative approach has been introduced by Kundu \textit{et al}, which yields effectively identical results. \cite{Kundu2022}

@@

These integrals, along with some relevant Franck-Condon factors, are plotted below as a function of offset.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/fcht.png}
	\caption{Plots of select (a) Franck-Condon factors and (b) Herzberg-Teller integrals relevant to this manuscript as a function of offset, $\Delta$.} 
	\label{fig:fcht}
\end{figure}

\newpage
\section{Impact of displacement, resonance frequencies, vibronic linewidth and molecular parameters on HDFG Spectra}
Inspection of the $A,B$ terms in the main text show that the HDFG output is dependent upon the relative size of products of Franck-Condon and Herzberg-Teller integrals.
For clarity, we plot the relevant product factors to assist in understanding the impact of offset on the HDFG spectra.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/fcht_product.png}
	\caption{Products of Franck-Condon and Herzberg-Teller integrals relevant to the $A, B_1, B_2$ terms in this manuscript as a function of offset, $\Delta$.} 
	\label{fig:fcht_product}
\end{figure}

These plots highlight the important distinction that $B$ term contributions to HDFG can dominate in the limit of small offset.
This is expected, as when $\Delta \rightarrow 0$, the overlap integral \autoref{key} resolves into the typical harmonic oscillator selection rules.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/changedelta.png}
	\caption{The impact of offset, vibrational resonance, and linewidth on HDFG spectra. Parameters for (a,b) follow from Myers et al., whereas parameters for (c,d) follow from Brennan et al.\cite{Myers1982, Brennan2024}
	Note that in these plots, the ratio $\abs{A/B} = 0.1$ is enforced} 
	\label{fig:chgdelta}
\end{figure}

@@

\section{Evaluating impact of static inhomogeneity on HDFG output}
In this section, the integral
\begin{equation}\label{generalcontour}
	\begin{split}
		\gamma_{ijkl} &= \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)\\
		&= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\eta_{ijkl}}{\left(\Delta_{ga} - \xi\right)\left(\Delta_{ba}+ c\xi\right)} \\
		&= \frac{\eta_{ijkl} \sigma}{\pi} \int_{-\infty}^\infty \mathrm{d}\xi\frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} + c\xi}\\
	\end{split}
\end{equation}
is evaluated for $c=-1$ (electronic state and vibrational state energy fluctuations are anti-correlated) and $c=1$ (electronic state and vibrational state energy fluctuations are correlated).
